---
title: Solution for Chapter 03 of Mastering Shiny
author: Chao Cheng
output: html_document
runtime: shiny
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

1.  When space is at a premium, it's useful to label text boxes using a placeholder that appears *inside* the text entry area.
    How do you call `textInput()` to generate the UI below?

    ```{r, echo = FALSE, out.width = NULL, message = FALSE}
    ui <- fluidPage(
      textInput("name", NULL, placeholder = "Your name")
    )
    # demo <- demoApp$new("basic-ui/placeholder", ui)
    # demo$takeScreenshot()
    ```
    
    __Solution:__ 
    ```{r, echo = TRUE, message = FALSE}
    ui <- fluidPage(
      textInput("name", NULL, placeholder = "Your name")
    )
    ```
    
    ```{r, eval = TRUE, echo = FALSE}
    textInput("name", NULL, placeholder = "Your name")
    ```
    
2.  Carefully read the documentation for `sliderInput()` to figure out how to create a date slider, as shown below.

    ```{r, echo = FALSE, out.width = NULL, message = FALSE}
    today <- as.Date("2021-01-01")
    ui <- fluidPage(
      sliderInput("delivery", "When should we deliver?", 
        value = today + 1, 
        min = today, 
        max = today + 7, 
        step = 1, 
        round = TRUE
      )
    )
    # demo <- demoApp$new("basic-ui/date-slider", ui)
    # demo$takeScreenshot()
    ```
    
    __Solution:__
    
    ```{r, echo = TRUE}
    today <- as.Date("2021-01-01")
    ui <- fluidPage(
      sliderInput("delivery", "When should we deliver?", 
        value = today + 1, 
        min = today, 
        max = today + 7, 
        step = 1, 
        round = TRUE
      )
    )
    ```
    
    ```{r, eval = TRUE, echo = FALSE}
    today <- as.Date("2021-01-01")
    sliderInput("delivery", "When should we deliver?", 
        value = today + 1, 
        min = today, 
        max = today + 7, 
        step = 1, 
        round = TRUE
      )
    ```
    
3.  If you have a moderately long list, it's useful to create sub-headings that break the list up into pieces.
    Read the documentation for `selectInput()` to figure out how.
    (Hint: the underlying HTML is called `<optgroup>`.)

    __Solution:__
    
    ```{r, echo = TRUE}
    long_group_list <- list(group1 = as.list(paste("list", 1 : 9, sep = "")), 
                            group2 = as.list(letters))
    ui <- fluidPage(selectInput("longlist", "select from a long list", 
                                choices = long_group_list))
    ```
    
    ```{r, eval = TRUE, echo = FALSE}
    long_group_list <- list(group1 = as.list(paste("list", 1 : 9, sep = "")), 
                            group2 = as.list(letters))
    selectInput("longlist", "select from a long list", 
                                choices = long_group_list)
    ```
    
4.  Create a slider input to select values between 0 and 100 where the interval between each selectable value on the slider is 5.
    Then, add animation to the input widget so when the user presses play the input widget scrolls through automatically.
    
    __Solution:__
    
    ```{r, echo = TRUE}
    ui <- fluidPage(sliderInput("select values", "select an input", 
                min = 0, max = 100, value = 0, step = 5, 
                animate = animationOptions(interval = 300, loop = TRUE)))
    ```
    
    ```{r, eval = TRUE, echo = FALSE}
    sliderInput("select values", "select an input", 
                min = 0, max = 100, value = 0, step = 5, 
                animate = animationOptions(interval = 300, loop = TRUE))
    ```
    
5.  Using the following numeric input box the user can enter any value between 0 and 1000.
    What is the purpose of the step argument in this widget?

    ```{r eval=FALSE}
    numericInput("number", "Select a value", value = 150, min = 0, max = 1000, step = 50)
    ```
    
    __Solution:__
    
    `step` controls the interval to use when stepping between min and max.
    
    ```{r, eval = TRUE, echo = FALSE}
    numericInput("number1", "Number input without step", value = 150, min = 0, max = 1000, step = NA)
    
    numericInput("number2", "Number input with step = 50", value = 150, min = 0, max = 1000, step = 50)
    ```